%=====================================
\section{High Volume Automated Testing}

\begin{frame}
  \frametitle{What Is High Volume Test Automation?}
  Tests that algorithmically generate, execute, evaluate, and summarize the results of arbitrarily many test actions on a system, in such volume as to:
  \begin{enumerate}
  \item Exceed the volume a reasonable testing staff could do manually.
  \item Expose behaviors of the system not normally exposed during traditional testing techniques.
  \item Simulate (ab)use of the system more realistically and dynamically than would be attainable through traditional techniques.
  \item Generate test scenarios that are not outside the realm of possibility or even probability due to the high-availability nature of modern software systems.
\end{enumerate}\nocite{KanerHivatOverview}
\end{frame}

%------------------
\subsection{Anatomy}

\begin{frame}
  \frametitle{Generators}
  \begin{itemize}
    \item How you hook up the RNG to the SUT.
    \item In short, how the test drives the System.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Interface}
  \begin{itemize}
    \item Black box?
    \item White box?
    \item In between? (hitting an HTTP api that's not public but also not unit-ey)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Oracle}
  \begin{itemize}
    \item How do you know if you've exposed bad behavior?
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Loggers and Diagnostics}
  \begin{itemize}
    \item How you know what happened.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Context}
  \begin{itemize}
    \item What are you trying to do? Corner a bug? Survey the system? Abuse the system?
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Scalability}
  \begin{itemize}
    \item Single-threaded? Many-threaded? Hammering the system from thousands of cloud servers?
  \end{itemize}\cite{parveen2010migrate}
\end{frame}

%------------------
\subsection{History}

\begin{frame}
  \frametitle{Inventors One Through Three}
  \begin{itemize}
    \item HP, "evil", 1966
    \item TI
    \item Bell
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Inventors Four Through Six (And Beyond)}
  \begin{itemize}
    \item Microsoft
    \item Telenova
    \item Fuzz Tester \cite{miller1989TR830}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Everybody Thinks It's A Trade Secret}
  \begin{itemize}
    \item Why wouldn't they?
    \item It's massively better at testing than what they read about.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{A Call For Academic Consideration}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

%------------------------
\subsection{Family Tree}

\begin{frame}
  \frametitle{Family Tree: Exploring (And Abusing) The Anatomy}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Long Sequence Regression Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{State Model Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Exhastive Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Fuzz Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Load Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Testing In Production}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{A/B Testing}
  \begin{itemize}
    \item TBD
  \end{itemize}\cite{HBR2017ABTest}
\end{frame}

%-------------------------------
\subsection{The Case for Yeager}

\begin{frame}
  \frametitle{Model-Based LSRT}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Quick To Implement}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Good Enough Detail}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Benefit From Existing Test Code}
  \begin{itemize}
    \item TBD
  \end{itemize}
\end{frame}
