%%-----------Acknowledgements---------------
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgments}
This thesis would not exist if not for the assistance of:
\begin{itemize}
    \item Dr. Cem Kaner and the Center For Software Testing Education and Research, for taking a chance on an enthusiastic freshman and introducing me to the world of software testing, as well as years of world-class training beyond valuation.

    \item The wider context-driven testing community, particularly the participants in the Workshops on Teaching Software Testing 11 and 12, my first exposure to the considerable ups and downs of academia.

    \item Ana Marafuga, Mike DeCabia, Jeff Farr, and Curtis Chambers, and the team at Dycom Industries, the most formative internship I've ever had. They let an intern design their entire corporate test automation strategy, most of which informed this thesis, brave souls all.

    \item Dr. Richard Ford, whose infectious enthusiasm for others' learning and discovery knows no bounds.

    \item The Samuels family, particularly Bill Jr. and Rob, and Dave Pickerell, for their helpful contributions through most of my academic tribulations.

    \item The members of the Ruckus and the Harbor City Hooligans. Soccer clubs typically lack rigor, but on the space coast everybody's a rocket scientist.

    \item My immediate and adopted family, for loving me to where I am today, including

    \item kbg, for reminding me to thank them for it.
\end{itemize}
